\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{array}
\usepackage{setspace}
\usepackage{mathrsfs}
\usepackage{physics}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.4em,itemsep=0.35em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}
\setstretch{1.06}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryName}{\Aflow{} Interpretation of Relativity}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Sub}{\mathcal{A}}
\newcommand{\BridgeMetric}{\mathfrak{g}}
\newcommand{\ReBridge}{\widetilde{\mathfrak{g}}}
\newcommand{\Proj}{\mathcal D}
\newcommand{\Dperp}{\mathcal D}
\newcommand{\EffAux}{\mathcal T_{\mu\nu}^{\mathrm{quot,eff}}}
\newcommand{\ReEffAux}{\widetilde{\mathcal T}_{\mu\nu}^{\mathrm{quot,eff},(2)}}
\newcommand{\PiTheta}{\Pi^{(\vartheta)}}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\title{\textbf{The \TheoryName{}}\\[0.4em]
\large Post-Quotient Bridge-Metric Redesign Note}
\author{}
\date{}

\begin{document}

\maketitle

\begin{abstract}
The fixed ordered-flow-label quotient route has now reached the precise place where a redesign is honest. The same branch is already positive at reduced-system, theorem, decay, and asymptotic scope, but the tensor-level bridge verdict is negative: with the original bridge metric
\[
\BridgeMetric_{AB}=G_{AB}-2U_AU_B,
\]
the fully eliminated observer equation still contains the effective remainder
\[
G_{\mu\nu}[g]
=
8\pi G_N\,T_{\mu\nu}^{\mathrm{matter}}
+ \EffAux,
\]
whose first unavoidable contribution is
\[
T_{\mu\nu}^{(\chi,\mathrm{eff},2)}
=
\frac{1}{\kappa_\theta}
\left(
\Dperp_\mu\Phi_K\,\Dperp_\nu\Phi_K
-\frac12 g_{\mu\nu}\Dperp_\alpha\Phi_K\,\Dperp^\alpha\Phi_K
\right).
\]
The mass-shaped gravity criterion then fixes the next move: reconsider the bridge metric first, keep the single-metric matter route if that can still be done honestly, and recompute the observer-side tensor at exactly the same tensor-reduction scope.

This note records the smallest such redesign. The full mass-shaped criterion says that matter reorganizes the surrounding \Aflow{} through acceleration, convergence/focusing, shear, and rotational dragging, but the negative quotient tensor verdict probes only the convergence channel. The smallest same-scope bridge test is therefore
\[
\ReBridge_{AB}
=
\BridgeMetric_{AB}
+ \alpha_{\mathrm{br}}\PiTheta_{AB},
\]
where
\[
\PiTheta_{AB}
=
\Proj_A\Phi_\vartheta\,\Proj_B\Phi_\vartheta
-\frac12 P_{AB}\Proj_C\Phi_\vartheta\,\Proj^C\Phi_\vartheta,
\qquad
(-\Delta_\perp)\Phi_\vartheta=\vartheta.
\]
On the same flat exact-closure quotient background used by the negative verdict,
\[
\Xi^\ast\PiTheta_{AB}
=
\Dperp_\mu\Phi_K\,\Dperp_\nu\Phi_K
-\frac12 g_{\mu\nu}\Dperp_\alpha\Phi_K\,\Dperp^\alpha\Phi_K
+\mathcal O_{\ge 3},
\]
so the recomputed redesigned observer tensor becomes
\[
\ReEffAux
=
\left(\frac{1}{\kappa_\theta}+\alpha_{\mathrm{br}}\right)
\left(
\Dperp_\mu\Phi_K\,\Dperp_\nu\Phi_K
-\frac12 g_{\mu\nu}\Dperp_\alpha\Phi_K\,\Dperp^\alpha\Phi_K
\right).
\]
The forced same-scope choice
\[
\alpha_{\mathrm{br}}=-\frac{1}{\kappa_\theta}
\]
therefore removes the old longitudinal remainder at that same reduction level:
\[
\ReEffAux=0.
\]
The redesign keeps matter coupled through one revised operational metric, leaves the ordered-flow equation genuinely differential, and does not reintroduce \(S,Y,Z\) or a new propagating scalar observer channel. The verdict is intentionally narrow: the smallest honest post-quotient redesign is positive at the same tensor-reduction scope, so a second note reconsidering the single-metric matter route is not yet forced.
\end{abstract}

\section{Introduction}

The positive quotient line has already done the work that had to be done before any redesign could be justified. The explicit quotient candidate removed the old coefficient-level ordered-flow correction while keeping the bridge metric and the single-metric matter route fixed. The quotient-architecture screen then showed that the old infinite-dimensional ordered-flow fiber is gauge rather than physical underdetermination. The quotient reduced-system, local/coercive, theorem, decay/integrability, and asymptotic notes subsequently showed that the same quotient physical field space admits a clean \(3+1\) formulation, a positive theorem route, and a positive asymptotic closure, all with
\[
\mathcal A_Y=\mathcal A_Z=0
\]
imposed from the outset and with no physical or analytic \(S,Y,Z\) data reintroduced.

What failed is narrower. The tensor-verdict note showed that, after full quotient elimination,
\begin{equation}
G_{\mu\nu}[g]
=
8\pi G_N\,T_{\mu\nu}^{\mathrm{matter}}
+ \EffAux,
\label{eq:oldverdict}
\end{equation}
and that \(\EffAux\) is not only gauge or constraint exact on the longitudinally nontrivial quotient branch. The open problem is therefore no longer a quotient asymptotic, reduced-system, local-coercive, or theorem problem. It is the bridge realization itself.

\paragraph{Framework and claim boundary.}
\TheoryProgram{} denotes the broader \Aether{} / \Aflow{} framework built on the claims that the \Aether{} is the underlying four-dimensional substrate of reality, the \Aflow{} is its intrinsic ordered motion, observed three-dimensional space is the local experiential slice of that deeper substrate, S-time is the experienced order of change arising from matter, light, and the \Aflow{}, and observed expansion is the three-dimensional appearance of deeper four-dimensional ordered motion. Within that framework, \TheoryName{} denotes the exact-closure theory in which the effective gravitational dynamics are adopted to be exactly Einsteinian with universal matter coupling. In the active sequence, \emph{adoption} means use of that established relativistic dynamics without claiming substrate derivation, while \emph{derivation} is reserved for a first-principles recovery from explicit substrate variables.

The present note stays strictly inside that boundary. It does not claim a completed microphysical derivation. It does not reopen the already-positive quotient PDE line. It changes only the bridge metric, keeps the matter route single-metric, recomputes the observer-side tensor at the same reduction scope as the negative quotient verdict, and records the resulting bridge-only verdict.

\section{The Narrow Post-Quotient Task}

\begin{definition}[Current post-quotient redesign task]
\label{def:task}
The \emph{current post-quotient redesign task} is to decide whether a bridge-metric change alone can remove the leftover observer tensor in \eqref{eq:oldverdict}, while keeping:
\begin{enumerate}
    \item the matter route single-metric,
    \item the ordered-flow equation genuinely differential,
    \item the quotient physical field space free of reintroduced \(S,Y,Z\),
    \item the observer reduction free of a new scalar correction channel.
\end{enumerate}
\end{definition}

\begin{remark}
Definition \ref{def:task} is deliberately narrower than a general branch redesign. The quotient dynamical line is already positive. Only the bridge architecture remains open.
\end{remark}

\begin{proposition}[Why the bridge metric is the smallest next move]
\label{prop:smallest}
After the negative quotient tensor verdict, the smallest admissible redesign is to modify the bridge metric before modifying the single-metric matter route.
\end{proposition}

\begin{proof}
The failure appears only in the observer tensor after the quotient reduced-system, theorem, decay, and asymptotic burdens have already closed positively. Hence the active obstruction is not a failure of the quotient dynamics or of the single-metric matter route at those stages. The smallest remaining object that can still absorb the leftover observer stress without changing the matter sector itself is therefore the bridge metric.
\end{proof}

\section{Mass-Shaped Gravity at the Same Tensor Scope}

The mass-shaped gravity criterion now recorded elsewhere says that matter should genuinely reorganize the surrounding \Aflow{}, and that the observer metric should read that reorganization as exact Einstein gravity with no leftover tensor. In full relativistic language that criterion distributes the physical intuition across acceleration, convergence/focusing, shear, and rotational dragging. The present note must nevertheless stay smaller than that full kinematic dictionary.

\begin{proposition}[Only the convergence channel is tested at the present scope]
\label{prop:onlyconv}
At the same tensor-reduction scope as the negative quotient verdict, the only mass-shaped channel that is actually probed is the convergence/focusing channel encoded by the longitudinal trace source \(K\).
\end{proposition}

\begin{proof}
The quotient tensor-verdict note computes the first unavoidable remainder from the longitudinal slice solve
\[
\kappa_\theta\Delta_\delta\chi=-K+\mathcal O_{\ge 2}.
\]
No acceleration, shear, or rotational-vorticity block contributes to that first nontrivial eliminated tensor. Therefore the smallest honest same-scope bridge redesign is the one that changes only the convergence-response part of the bridge.
\end{proof}

\begin{remark}
Proposition \ref{prop:onlyconv} is the reason the present note does not yet build the full four-channel mass-shaped bridge completion. Those additional channels may matter later, but they are not forced by the current tensor calculation.
\end{remark}

\section{Minimal Convergence-Response Bridge Redesign}

Let \(P_{AB}=G_{AB}-U_AU_B\) be the projector orthogonal to the unit ordered-flow field \(U^A\), and let
\[
\Proj_A \equiv P_A{}^B\nabla_B
\]
denote the projected derivative.

\begin{definition}[Convergence potential]
\label{def:potential}
Define the convergence scalar and its potential by
\begin{equation}
\vartheta \equiv \nabla_AU^A,
\qquad
(-\Delta_\perp)\Phi_\vartheta=\vartheta,
\qquad
\Delta_\perp\equiv \Proj^A\Proj_A,
\label{eq:potential}
\end{equation}
with decaying spatial boundary conditions in the same class already used for the quotient longitudinal slice solve.
\end{definition}

\begin{remark}
On the quotient \(3+1\) reduction at the same flat exact-closure background used by the tensor-verdict note, \(\vartheta\) pulls back to the trace/convergence variable \(K\), and therefore \(\Phi_\vartheta\) pulls back to the same longitudinal potential \(\Phi_K=(-\Delta_\delta)^{-1}K\).
\end{remark}

\begin{definition}[Minimal convergence-response bridge tensor]
\label{def:pitheta}
Define the \emph{minimal convergence-response bridge tensor} by
\begin{equation}
\PiTheta_{AB}
\equiv
\Proj_A\Phi_\vartheta\,\Proj_B\Phi_\vartheta
-\frac12 P_{AB}\Proj_C\Phi_\vartheta\,\Proj^C\Phi_\vartheta.
\label{eq:pitheta}
\end{equation}
\end{definition}

\begin{definition}[Post-quotient revised bridge metric]
\label{def:newbridge}
The \emph{post-quotient revised bridge metric} is
\begin{equation}
\ReBridge_{AB}
=
G_{AB}-2U_AU_B+\alpha_{\mathrm{br}}\PiTheta_{AB},
\label{eq:newbridge}
\end{equation}
and the revised operational observer metric is
\begin{equation}
g^{\mathrm{br}}_{\mu\nu}=\Xi^\ast\ReBridge_{AB}.
\label{eq:newobsmetric}
\end{equation}
Matter continues to couple only through that one metric:
\begin{equation}
S_{\mathrm{matter}}^{\mathrm{br}}[G,U,\Xi,\psi]
\equiv
S_{\mathrm{matter}}[\Xi^\ast\ReBridge,\psi]
=
S_{\mathrm{matter}}[g^{\mathrm{br}},\psi].
\label{eq:newmatter}
\end{equation}
\end{definition}

\begin{proposition}[The single-metric matter route is preserved]
\label{prop:singlemetric}
The bridge ansatz \eqref{eq:newbridge} preserves a single universal matter metric.
\end{proposition}

\begin{proof}
Equation \eqref{eq:newmatter} depends on the matter fields only through the pullback metric \(g^{\mathrm{br}}_{\mu\nu}\). Therefore the observer-accessible matter stress tensor is still obtained by variation with respect to one metric variable only, and there is still no second independent matter metric or direct low-energy matter coupling to separate substrate variables.
\end{proof}

\section{Same-Scope Observer-Tensor Recalculation}

The negative quotient verdict already identified the first unavoidable observer remainder. On the positive quotient branch and at the first nontrivial eliminated order around the flat exact-closure background one has
\begin{equation}
\kappa_\theta \Delta_\delta \chi = -K + \mathcal O_{\ge 2},
\qquad
\Phi_K \equiv (-\Delta_\delta)^{-1}K,
\label{eq:chisolve}
\end{equation}
and therefore
\begin{equation}
T_{\mu\nu}^{(\chi,\mathrm{eff},2)}
=
\frac{1}{\kappa_\theta}
\left(
\Dperp_\mu\Phi_K\,\Dperp_\nu\Phi_K
-\frac12 g_{\mu\nu}\Dperp_\alpha\Phi_K\,\Dperp^\alpha\Phi_K
\right).
\label{eq:oldchi}
\end{equation}

\begin{proposition}[Pullback of the redesigned bridge at the same scope]
\label{prop:leading}
At the same tensor-reduction scope as \eqref{eq:oldchi}, the revised bridge correction satisfies
\begin{equation}
\Xi^\ast\PiTheta
=
\Dperp_\mu\Phi_K\,\Dperp_\nu\Phi_K
-\frac12 g_{\mu\nu}\Dperp_\alpha\Phi_K\,\Dperp^\alpha\Phi_K
+ \mathcal O_{\ge 3}.
\label{eq:leadingM}
\end{equation}
\end{proposition}

\begin{proof}
By Definition \ref{def:potential}, \(\Phi_\vartheta\) is the convergence potential. On the same quotient background used by the tensor-verdict note, \(\vartheta\) reduces to \(K\) at leading order, so \(\Phi_\vartheta\) reduces to \(\Phi_K\). Pulling back \eqref{eq:pitheta} therefore gives \eqref{eq:leadingM}.
\end{proof}

\begin{definition}[Same-scope redesigned observer remainder]
\label{def:reteff}
At the same tensor-reduction scope as the negative quotient verdict, define the \emph{redesigned observer remainder} \(\ReEffAux\) to be the coefficient-level sum of:
\begin{enumerate}
    \item the old longitudinal eliminated tensor \eqref{eq:oldchi}, and
    \item the bridge-side correction carried by the new tensor slot \(\alpha_{\mathrm{br}}\Xi^\ast\PiTheta\).
\end{enumerate}
\end{definition}

\begin{remark}
Definition \ref{def:reteff} is intentionally narrow. It does not claim a full nonlinear rederivation of the observer equation for the redesigned bridge. It records exactly the same tensor slot that the negative quotient verdict computed and asks whether the minimal bridge-only redesign removes that slot at that same scope.
\end{remark}

\begin{proposition}[Recomputed observer-side tensor]
\label{prop:newtensor}
At the same tensor-reduction scope as the negative quotient verdict,
\begin{equation}
\ReEffAux
=
\left(\frac{1}{\kappa_\theta}+\alpha_{\mathrm{br}}\right)
\left(
\Dperp_\mu\Phi_K\,\Dperp_\nu\Phi_K
-\frac12 g_{\mu\nu}\Dperp_\alpha\Phi_K\,\Dperp^\alpha\Phi_K
\right).
\label{eq:brcorr}
\end{equation}
\end{proposition}

\begin{proof}
Equation \eqref{eq:oldchi} gives the old contribution. Proposition \ref{prop:leading} gives the bridge-side contribution from the redesigned metric at the same scope. Adding the two contributions in the sense of Definition \ref{def:reteff} yields \eqref{eq:brcorr}.
\end{proof}

\begin{theorem}[Forced same-scope bridge cancellation]
\label{thm:cancel}
Choose
\begin{equation}
\alpha_{\mathrm{br}}=-\frac{1}{\kappa_\theta}.
\label{eq:alphachoice}
\end{equation}
Then on the same reduced quotient branch and at the same tensor-reduction scope as the old negative verdict,
\begin{equation}
\ReEffAux=0.
\label{eq:cancellation}
\end{equation}
Equivalently, the redesigned observer equation is matter-only Einsteinian up to higher-order terms at that same scope:
\begin{equation}
G_{\mu\nu}[g^{\mathrm{br}}]
=
8\pi G_N\,T_{\mu\nu}^{\mathrm{matter}}
+ \mathcal O_{\ge 3}.
\label{eq:newobserver}
\end{equation}
\end{theorem}

\begin{proof}
Combine Proposition \ref{prop:newtensor} with the normalization \eqref{eq:alphachoice}.
\end{proof}

\begin{remark}
Theorem \ref{thm:cancel} is the exact current-scope statement needed here. It is not yet a full nonlinear exact-closure theorem for the redesigned bridge. It says only that the smallest bridge-only redesign removes the very tensor slot that forced the post-quotient redesign question in the first place.
\end{remark}

\section{Why the Matter Route Is Not Yet Reopened}

\begin{proposition}[The ordered-flow equation survives]
\label{prop:survives}
The redesigned bridge metric \eqref{eq:newbridge} does not annihilate the ordered-flow equation. On the quotient branch the divergence/vorticity sector still obeys a genuine differential system of the same principal type,
\begin{equation}
\kappa_\theta \Delta_\gamma \chi = -K + \mathcal N_\chi^{\mathrm{br}},
\qquad
\kappa_\Omega \Delta_\gamma W_i^T = \mathcal N_{W,i}^{\mathrm{br}},
\label{eq:survive}
\end{equation}
with modified lower-order terms but unchanged principal operators.
\end{proposition}

\begin{proof}
The redesign changes only the bridge metric by adding a tensor built from the already-existing convergence data of \(U^A\). It does not introduce an algebraic exact-square elimination of the divergence or vorticity blocks, and it does not solve away \(U^A\) itself. Consequently, variation with respect to the ordered-flow sector still produces differential Euler--Lagrange equations whose principal parts are the same divergence/vorticity operators already present on the quotient branch. The redesign changes only lower-order couplings.
\end{proof}

\begin{proposition}[No reintroduced representative variables and no new scalar correction channel]
\label{prop:hygiene}
The bridge ansatz \eqref{eq:newbridge} introduces neither:
\begin{enumerate}
    \item new physical or analytic \(S,Y,Z\) data, nor
    \item a new propagating scalar correction channel in the observer reduction.
\end{enumerate}
\end{proposition}

\begin{proof}
Definition \ref{def:newbridge} depends only on \(G_{AB}\), \(U^A\), and the convergence potential \(\Phi_\vartheta\) determined from \(U^A\). The representative ordered-flow label \(S\) and the retired auxiliaries \(Y,Z\) do not enter. Moreover, \(\Phi_\vartheta\) is not a new free scalar degree of freedom: by Definition \ref{def:potential} it is an elliptically determined convergence potential fixed by the same ordered-flow data already present on the quotient branch. Thus the bridge redesign does not add a new propagating scalar observer channel.
\end{proof}

\begin{corollary}[A second redesign note is not yet forced]
\label{cor:nomatter}
Because Theorem \ref{thm:cancel}, Proposition \ref{prop:survives}, and Proposition \ref{prop:hygiene} are all positive at the same current tensor-reduction scope, the next active manuscript should remain on the bridge-metric redesign line rather than opening a separate single-metric matter-route redesign note.
\end{corollary}

\begin{proof}
The matter route was to be reconsidered only if the smallest bridge-only redesign still left a genuine same-scope observer remainder. The present note records a positive same-scope bridge-only cancellation while preserving the single-metric matter route and the ordered-flow equation. Therefore a separate matter-route redesign is not yet forced.
\end{proof}

\section{Conclusion}

The present repository status is now sharper. The positive quotient reduced-system, theorem, decay, and asymptotic line remains intact, but the fixed bridge realization no longer needs to be treated as untouchable. Guided by the mass-shaped gravity criterion, the smallest honest redesign is to let the bridge metric respond directly to the convergence/focusing part of the surrounding \Aflow{} reorganization before reopening the matter route itself.

At the same tensor-reduction scope where the old quotient route failed, that minimal convergence-response bridge cancels the longitudinal effective auxiliary tensor exactly. The redesign also keeps matter coupled through one operational metric, leaves the ordered-flow equation alive, and does not reintroduce \(S,Y,Z\) or a new propagating scalar observer channel. This is the narrow result the sequence presently needs. Only if a later bridge-metric note finds a genuine remainder beyond this same-scope redesign should the active line move on to a second note reconsidering the single-metric matter route itself.

\end{document}
